\documentclass[12pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
\usepackage{graphicx}
\usepackage{color}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{CSE 430 Homework 7}
\author{Ryan Dougherty}
\date{}                                           % Activate to display a given date or no date

\begin{document}
\maketitle

\section*{Question 10.6}{\color{blue}Is there any way to implement truly stable storage? Explain your answer.}

\section*{Question 10.11}{\color{blue}Suppose that a disk drive has 5,000 cylinders, numbered 0 to 4,999. The drive is currently serving a request at cylinder 2,150, and the previous request was at cylinder 1,805. The queue of pending requests, in FIFO order, is:
\begin{center}
2,069, 1,212, 2,296, 2,800, 544, 1,618, 356, 1,523, 4,965, 3681
\end{center}
Starting from the current head position, what is the total distance (in cylinders) that the disk arm moves to satisfy all the pending requests for each of the following disk-scheduling algorithms?
\begin{enumerate}
\item[(a)]FCFS
\item[(b)]SSTF
\item[(c)]SCAN
\item[(d)]LOOK
\item[(e)]C-SCAN
\item[(f)]C-LOOK
\end{enumerate}
}

\section*{Question 10.14}{\color{blue}Describe some advantages and disadvantages of using SSDs as a caching tier and as a disk-drive replacement compared with using only magnetic disks.}

\section*{Question 10.17}{\color{blue}Consider a RAID level 5 organization comprising five disks, with the parity for sets of four blocks on four disks stored on the fifth disk. How many blocks are accessed in order to perform the following?
\begin{enumerate}
\item[(a)]A write of one block of data
\item[(b)]A write of seven continous blocks of data
\end{enumerate}

\end{document}  